### 2009-10-29 doc/manuals/user_interface/ui-conf.tex
Broker name sync with the current broker loader name
Added brokers description as a separate file, other small fixes

Configures which brokering algorithm to use during job submission. This attribute
corresponds to the \verb#-b# command line option. The
default one is the \texttt{Random} broker that chooses targets randomly.
Another possibility is, for example, the \texttt{FastestQueue} broker that
chooses the target with the shortest estimated queue waiting time. Possible
values are:
\begin{itemize}
 \item[\texttt{Random}] -- ranks targets randomly (default)
 \item[\texttt{FastestQueue}] -- ranks targets according to their queue length
% \item[\texttt{FastestCPU}] -- ranks targets according to CPU performance
 \item[\texttt{Data}] -- ranks target according the amount of megabytes of the
requested input files that are already in the computing resource’s cache.
% \item[\texttt{SampleBroker}] -- Ranks targets randomly (written in Python)
\end{itemize}

@@

This attribute is used in case a broker comes with arguments.

>>>>

Configures which brokering algorithm to use during job submission. This attribute
corresponds to the \verb#-b# command line option. The
default one is the \texttt{Random} broker that chooses targets randomly.
Another possibility is, for example, the \texttt{FastestQueue} broker that
chooses the target with the shortest estimated queue waiting time. For an 
overview of brokers, please refer to Section~\ref{sec:arcsub}.

@@

This attribute is used in case a broker comes with arguments. This corresponds to the
parameter that follows column in the \verb#-b# command line option.
